---
output:
    pdf_document:
      citation_package: natbib
      df_print: tibble
      fig_caption: yes
      keep_tex: no
      template: "../inst/extdata/markdown/latex-ms.tex"
title: 'sits.rep: Reproducibility of Satellite Image Time Series.'
author:
- affiliation: National Institute for Space Research (INPE), Brazil
  name: Rafael Mariano
- affiliation: National Institute for Space Research (INPE), Brazil
  name: Pedro R. Andrade
- affiliation: National Institute for Space Research (INPE), Brazil
  name: Gilberto Queiroz
date: "`r format(Sys.time(), '%B %d, %Y')`"
endnote: false
fontfamily: mathdesign
fontfamilyoptions: adobe-utopia
fontsize: 11pt
graphics: true
mathtools: true
vignette: |
  %\VignetteEncoding{UTF-8} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteIndexEntry{SITS: Data Analysis and Machine Learning using Satellite Image Time Series}
---

O sits.rep é um pacote para a linguagem R com o propósito de reproduzir as classificações e iterações pós classificação realizadas pelo pacote 

Este documento irá descrever duas funções do pacote sits.rep 

```{r setup, include=FALSE}

library(sits.rep)
```

## R Markdown



```{r cars}


sits.rep::sits.rep_classify("arv_1", "~/workspace/sits.rep/script/classification.R")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
sits.rep::sits.rep_reproduce("arv_1", "classification", "rep_deeplearnings")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
